Citeopotamus

### 2012-12-08 paper/paper.tex

>>>>

\subsection{Incorrect References}
Sometimes there is an error in scraping which causes a reference to take on the incorrect number.
To prevent these refernces from polluting our data, we check for them during parsing.
We parse the refernce section of the paper and look at every reference. If the reference does not contain all of the author names with
more than three letters, then we drop the reference and assume it is incorrect.
If there are no references left after all the references have been parsed, then the entire paper is droped.
Of our original 102O papers, 720 made it passed this phase.
